Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-08-10 analysis/report/effectiveness_report.Rmd
render md, html, and keep figures

---
title: "Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers"
output:
  html_document:
    code_folding: hide
    keep_md: yes
  pdf_document: default
  md_document:
    variant: gfm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

>>>>

---
title: "Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers"
output:
  github_document:
    keep_html: TRUE
  #  code_folding: hide
    #keep_md: yes
  #pdf_document: default
  # md_document:
  #   variant: gfm
  #html_document
---

```{r setup, include=FALSE}

@@

fs::dir_create(output_dir, "report", "figures")

knitr::opts_chunk$set(
  echo = TRUE,
  fig.path = paste0(fs::path(output_dir, "report", "figures"), "/")
)
